---
title: "Test R Markdown 1"
author: "Claire Campbell"
date: "2023-08-28"
output: html_document
---

Testing how to create reproducible R analyses.

Trying to use renv from [this site](https://appsilon.com/renv-how-to-manage-dependencies-in-r/).

# First must activate renv
Can either activate when making a new project or after by:
```{r eval=F}
renv::activate()
```


# Install packages to renv
Renv will pull libraries from a different folder than the R installed packages so can't used already installed packages.
```{r eval=F}
install.packages("dplyr")
install.packages("plotly")
```

# Take snapshot of environment
```{r}
renv::snapshot()
```

# Run code to test
This is from [Plotly documentation](https://plotly.com/r/bar-charts/)
```{r}
library(plotly)

x <- c("Product A", "Product B", "Product C")
y <- c(20, 14, 23)
y2 <- c(16, 12, 27)
text <- c("27% market share", "24% market share", "19% market share")
data <- data.frame(x, y, y2, text)

fig <- data %>% plot_ly()
fig <- fig %>% add_trace(
  x = ~x, y = ~y, type = "bar",
  text = y, textposition = "auto",
  marker = list(
    color = "rgb(158, 202, 225)",
    line = list(color = "rgb(8, 48, 107)", width = 1.5)
  )
)
fig <- fig %>% add_trace(
  x = ~x, y = ~y2, type = "bar",
  text = y2, textposition = "auto",
  marker = list(
    color = "rgb(58, 200, 225)",
    line = list(color = "rgb(8, 48, 107)", width = 1.5)
  )
)
fig <- fig %>% layout(
  title = "January 2013 Sales Report",
  barmode = "group",
  xaxis = list(title = ""),
  yaxis = list(title = "")
)

fig
```

# Now retake snapshot to update lockfile
```{r}
renv::snapshot()
```

# Transfer R project to Git
git init
git add .
git commit -m "initial commit"
git remote add origin https://github.com/theclairecamp/Reproducible_RProjects.git
git push -u origin main

# Restore R environment
git clone https://github.com/theclairecamp/Reproducible_RProjects.git TestReproducibility_RestoreRenv
open downloaded project *make sure not to run renv::activate() to override old renv.lock file (can always copy-replace over old renv.lock file with new one if accidentally run renv::activate())
run renv::restore() to restore R environment of project cloned
